---
title: README
format: gfm
---

# CAbiNet

**Correspondence Analysis based Biclustering on Networks - Bipartite graph version**

This package provides functions to for the visualization and biclustering of single-cell RNA-seq data.

This package is a modified version of the CAbiNet package: <https://github.com/ClemensKohl/CAbiNet>
Instead of building a cell-gene graph, a bipartite graph is used for biclustering.

A longer vignette explaining for the standard CAbiNet can be found here:
https://vingronlab.github.io/CAbiNet/

## Installation

You can install the package with:

```r
#| eval: false
#| label: installation
devtools::install_github("ClemensKohl/CAbiNetBIP")
```

> ⚠️ A bug in ggplot2 versions >3.3.0 and <3.4.1 lead to incorrect behaviour in `plot_hex_biMAP`. Please make sure you have ggplot2 3.4.1 or higher installed.

## Quick start

Here I provide a minimal example on how to use CAbiNetBIP:

### Setup
```r
#| label: setup
suppressPackageStartupMessages({
  library(CAbiNetBIP)
  library(APL)
  library(scRNAseq)
})

sce <- DarmanisBrainData()

# Here you might want to do some preprocessing.
```

### Biclustering
```{r}
#| label: CA

# Correspondence Analysis
caobj = cacomp(sce, dims = 50, top = 1000) # number of genes with highest inertia to keep.

# biclustering using the bipartite graph
cabic <- caclust_bip(
  obj = caobj,
  k = 10,
  min_edges = 50,
  MNN = FALSE,
  resolution = 1,
  algorithm = "leiden",
  leiden_pack = "leiden",
  method = BiocNeighbors::AnnoyParam()
)

sce$cabinet <- cell_clusters(cabic)
```

### Visualization
```{r}
#| label: bimap

# Create biMAP
cabic <- biMAP(cabic, caobj, k_umap = 10, rand_seed = 2358)
```

```{r}
#| label: plot
plot_biMAP(cabic, color_genes = TRUE)
```

```{r}
#| label: bimap2
plot_scatter_biMAP(
  cabic,
  gene_alpha = 0,
  color_by = "cell.type",
  meta_df = colData(sce)
)
```

### Interactive biMAP 
```{r}
#| label: interactive
plot_biMAP(cabic, color_by = "cluster", color_genes = TRUE, interactive = TRUE)
```

